Two NIRCam Arms are Better than One: How JWST Can Do More Science with NIRCam's Short-Wavelength Dispersed Hartmann Sensor

### 2016-07-08 ms.tex
I added figures for HAT-P-12b's clear atmosphere model.

\begin{figure}[!ht]
\includegraphics[width=0.5\textwidth]{molecules_DHS_HD209.pdf}
\caption{Model spectra separated by molecule for HD209458b.
The new DHS mode would allow simultaneous spectra at 1-2$\mu$m ``for free'' when observing with either NIRCam's F322W2 or F444W slitless grism observations in its long-wavelength arm.
The simulated data are for one transit in each of the long-wavelength grism modes, each accompanied by simultaneous DHS grism spectra.
The observations longer than 5$\mu$m are simulated for MIRI's Low Resolution Spectrometer.}\label{fig:DHSmolecules}
\end{figure}

@@

>>>>

\begin{figure}[!ht]
\includegraphics[width=0.5\textwidth]{molecules_DHS_HD209.pdf}
\caption{Model spectra separated by molecule for HD 209458b.
The new DHS mode would allow simultaneous spectra at 1-2$\mu$m ``for free'' when observing with either NIRCam's F322W2 or F444W slitless grism observations in its long-wavelength arm.
The simulated data are for one transit in each of the long-wavelength grism modes, each accompanied by simultaneous DHS grism spectra.
The observations longer than 5$\mu$m are simulated for MIRI's Low Resolution Spectrometer.}\label{fig:DHSmolecules}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{HAT-P-12b_kmr_clear_DHS_nc.pdf}
\caption{Model spectra separated by molecule for for the inflated warm Saturn HAT-P-12b.
Error bars shown are for simulated observation with the DHS grism, F322W2 and F444W modes, for a total of 2 transits or about 17 hours of JWST time.}\label{fig:DHSvsNIRISS209}
\end{figure}
